Managing variability in software systems

### 2021-04-22 Paper.tex
added variability planning
divide section workload

\section{Introduction}
Here we are going to introduce the reader into the broad environment

\section{Background and related work}
In this section the background research which we use to present an overview of the topic.

\section{Origin of variability}
We introduce why there is variability in the modern software engineering process. So that the reader knows how the problems arrise to have a baseline for presenting solutions for said problems.

\section{Variability modeling}
The question we want to answer in this section how one can model/describe the changes the software architecture is exposed to and how the dependencies and flexibility can be put into a defined state.

\section{Variability patterns}
Sums up the typical patterns how variability can be introduced.

\section{Discussion/Challenges}
Discuss why the variability of systems is hard to tackle and why it is not always successful.

\section{Conclussion}
Make final remarks about the discussed elements.

\begin{thebibliography}{00}
\bibitem{b1} Apel S., Batory D., Kästner C., Saake G. (2013) Software Product Lines. In: Feature-Oriented Software Product Lines. Springer, Berlin, Heidelberg. ISBN 978-3-642-37520-0
\bibitem{b2} J. van Gurp, J. Bosch and M. Svahnberg, "On the notion of variability in software product lines," Proceedings Working IEEE/IFIP Conference on Software Architecture, Amsterdam, Netherlands, 2001, pp. 45-54, doi: 10.1109/WICSA.2001.948406.
\bibitem{b3} Bachmann F., Bass L. (2001). Managing Variability in Software Architectures. Software Engineering Institute, Carnegie Mellon University.
\bibitem{b4} Galster M., Weyns D., Tofan  D., Bartosz M., Avgeriou P. (2014). Variability in Software Systems—A Systematic Literature Review. Software Engineering, IEEE Transactions on. 40. 282-306. 10.1109/TSE.2013.56. 
\end{thebibliography}

>>>>

\section{Introduction}
Here we are going to introduce the reader into the broad environment  
(1/2 page) JR

\section{Background and related work}
In this section the background research which we use to present an overview of the topic.
(1/2 page) NH

\section{Origin of variability}
We introduce why there is variability in the modern software engineering process. So that the reader knows how the problems arrise to have a baseline for presenting solutions for said problems.
(1/2 page) NH

\section{Variability modeling}
The question we want to answer in this section how one can model/describe the changes the software architecture is exposed to and how the dependencies and flexibility can be put into a defined state. 
(1 page) JR

\section{Variability patterns}
Sums up the typical patterns how variability can be introduced.
(1/2 page, maybe merge with section above) NH

\section{???Variability planning???}
Gives an overview of how someone can plan for varability and how to manage it.

\section{Discussion/Challenges}
Discuss why the variability of systems is hard to tackle and why it is not always successful.
(1/4 page) JR

\section{Conclussion}
Make final remarks about the discussed elements.
(1/4 page) NH

\begin{thebibliography}{00}
\bibitem{b1} S. Apel, D. Batory, C. Kästner and G. Saake, "Software Product Lines. In: Feature-Oriented Software Product Lines", Berlin Heidelberg, Springer (2013)
\bibitem{b2} J. van Gurp, J. Bosch and M. Svahnberg, "On the notion of variability in software product lines," Proceedings Working IEEE/IFIP Conference on Software Architecture", Amsterdam, Netherlands, 2001, pp. 45-54
\bibitem{b3} F. Bachmann, L. Bass, "Managing Variability in Software Architectures", Carnegie Mellon University (2001)
\bibitem{b4} M. Galster, D. Weyns, D. Tofan, M. Bartosz, P. Avgeriou, "Variability in Software Systems—A Systematic Literature Review", IEEE Transactions on Software Engineering (2014)
\bibitem{b5} T. Berger, J.-P. Steghöfer, T. Ziadi, J. Robin, and J. Martinez, "The state of adoption and the challenges of systematic variability management in industry", Empirical Software Engineering, vol. 25, pp. 1755-1797, 2020
\end{thebibliography}
